Kit Theory

### 2023-06-21 paper/paper.tex
Update.

  For example a term of type \texttt{[𝕖, 𝕥] ⊢ 𝕖} is an expression with two free variables, where variable 0 is a placeholder for an expression, and variable 1 for a type.
  \LibCode\KSortTy

@@

  \subsection{Unifying Renamings \& Substitutions}
  A well-known problem with DeBruijn-indices is that full substitution
  cannot be defined directly by structural recursion on the term.
  The typical workaround is to define renamings and substitutions
  separately and use renamings to weaken substitutions when going under binders.

@@

  \subsection{Library}
  \LibCode\KKit
  \LibCode\KMap
  \LibCode\KAp
  \LibCode\KExt
  \LibCode\KLift
  \LibCode\KId
  \LibCode\KSingle
  \LibCode\KWeaken
  \LibCode\KEq
  \LibCode\KFunExt
  \LibCode\KIdLift
  % \LibCode\KIdLiftProof
  \LibCode\KKitNotation
  \LibCode\KTraversal
  \LibCode\KKitInstances
  \LibCode\KKitOpen
  \subsection{System F}
  \AppCode\FTraversalOp
  \AppCode\FTraversalId
  \AppCode\FTraversalIdProofInteresting
  % \LibCode\FTraversalIdProofRest
  \AppCode\FTraversal

>>>>

  For example a term of type \texttt{[𝕥, 𝕥] ⊢ 𝕖} is an expression (\texttt{𝕖}) with two free type-variables (\texttt{𝕥}).
  \LibCode\KSortTy

@@

  \subsection{Unifying Renamings \& Substitutions}
  A well-known problem with DeBruijn-indices is that full substitution
  cannot be defined directly by structural recursion on the term.
  The typical workaround is to define renamings and substitutions
  separately and use renamings to weaken the terms in substitutions
  when going under binders.

@@

  In both cases \texttt{\_∋\_} and \texttt{\_⊢\_} are instanciated to type
  \texttt{List (Sort Var) → Sort Var → Set}, so we can create a structure
  to axiomatize the common theory behind both of them.
  \LibCode\KKit

  \subsection{Library}
  \LibCode\KMap
  \LibCode\KAp
  \LibCode\KExt
  \LibCode\KLift
  \LibCode\KId
  \LibCode\KSingle
  \LibCode\KWeaken
  \LibCode\KEq
  \LibCode\KFunExt
  \LibCode\KIdLift
  % \LibCode\KIdLiftProof
  \LibCode\KKitNotation
  \LibCode\KTraversal
  \LibCode\KKitInstances
  \LibCode\KKitOpen
  \subsection{System F}
  \AppCode\FTraversalOp
  \AppCode\FTraversalId
  \AppCode\FTraversalIdProofInteresting
  % \LibCode\FTraversalIdProofRest
  \AppCode\FTraversal
